Exploring the Relationship between Family Background and Children's Education Level in the United States (2021)

### 2023-04-17 outputs/paper/paper.qmd
tiny changes in the data cleaning

In addition, the variable of **degree** is grouped into two levels. For respondents who have obtained at least a degree from an associate/junior college, their levels are denoted as "1", indicating they have completed a post-secondary education. For respondents who have attained only a high school diploma or possess a lower level of education, their levels are designated as "0".

>>>>

In addition, the variable of **degree** is grouped into two levels. For respondents who have obtained at least a degree from an associate/junior college, their levels are denoted as "1", indicating they have completed a post-secondary education. This is because the logistic model only takes binary response variable. Hence, for respondents who have attained only a high school diploma or possess a lower level of education, their levels are labelled as "0".
